The number of lattices of Voronoi's first kind

### 2014-06-04 findsuperbase/findsuperbase.tex
added minor

As expected, all lattices generated in dimensions 1, 2, and 3 were found to be of Voronoi's first kind.  When $n=4$ roughtly 25\% of the lattices generated by methods 1 and 2 were of Voronoi's first kind, but none of the 500 bases generated by method 3 were of first kind.  I find this very interesting! The simulations suggest that the lattices of Voronoi's first kind do not lie within a space of measure zero with respect to the measures induced by the first two generation methods, but that they do lie on a space of measure zero with respect to the lattices that occur when converting complex valued MIMO channel matrices into real valued lattices bases.  This might suggest that lattices of first kind will (atleast not directly) be useful for MIMO.

I was too oppimistic when I thought I would be able to run this with $n=6$.  This would take too long with the existing code.  There are a number of optimisations that can be made that might make running simulations with $n=6$ possible.

>>>>

As expected, all lattices generated in dimensions 1, 2, and 3 were found to be of Voronoi's first kind.  When $n=4$ roughly 25\% of the lattices generated by methods 1 and 2 were of Voronoi's first kind, but none of the 500 bases generated by method 3 were of first kind.  I find this very interesting! The simulations suggest that the lattices of Voronoi's first kind do not lie within a space of measure zero with respect to the measures induced by the first two generation methods, but that they do lie on a space of measure zero with respect to the lattices that occur when converting complex valued MIMO channel matrices into real valued lattice bases.  This might suggest that lattices of first kind will not be useful for MIMO (at least not directly).

It would be interesting to see if these conclusion hold in higher dimension. I was too optimistic when I thought I would be able to run this with $n=6$.  This would take too long with the existing code.  There are a number of optimisations that can be made that might make running simulations with $n=6$ possible.
